Initial Analysis

### 2019-08-20 Initial_Analysis.Rmd
Updates on results

@@

TenFifty <- Results_Data %>% 
  filter(Model_Index >= 50#,
         # Trans_Index >= 0.10
         ) %>% 
  group_by(Name,Model_Index) %>% 
  summarise(
    n_trans = length(unique(TaxonKey)),
    n_countries = length(unique(Neighbor_Territory))
    ) 
  filter(Model_Index == 100)
  # head(Results_Data)

@@

World_EEZs_simple <- World_EEZs %>% 
  st_transform(crs = 4326) %>% # 4326
  st_simplify(preserveTopology = TRUE, dTolerance = 1) %>%
  left_join(TenFifty, by ="Name") %>%
  filter(!is.na(n_Trans_Spp)) #%>%
  # st_transform(crs = 3832)

@@

Plot <- ggplot(World_EEZs_simple) +
  geom_sf(aes(fill = n_Trans_Spp)) +
  scale_fill_gradientn(colours = pal) +
  ggtheme_map()

ggsave("MI_100_TI_all_plot.png",
       plot = Plot,
       width = 16,
       height = 8,
       units = "in",
       path = "/Volumes/DATA/JULIANO_NEYMAR/FishForVisa/Figures/"
)

>>>>

Clean_Results <- Results_Data %>% 
  filter(is.na(Trans_Index)) %>% 
  select(1:5)

length(unique(Clean_Results$TaxonKey))

head(Clean_Results)
```

@@

TenFifty <- Clean_Results %>% 
  filter(Model_Index == 100,
         Area_Index >= 0.25,
         Area_Index <= 0.75
         ) %>% 
  group_by(Name=Country_Territory,Model_Index) %>% 
  summarise(
    n_trans = length(unique(TaxonKey)),
    n_countries = length(unique(Neighbor_Territory))
    ) 
  filter(Model_Index == 100)
  # head(Results_Data)

@@

World_EEZs_simple <- World_EEZs %>% 
  st_transform(crs = 4326) %>% # 4326
  st_simplify(preserveTopology = TRUE, dTolerance = 0.1) %>%
  left_join(TenFifty, by ="Name") #%>%
  # filter(!is.na(n_trans)) #%>%
  # st_transform(crs = 3832)

@@

Plot <- ggplot(World_EEZs_simple) +
  geom_sf(aes(fill = n_trans)) +
  scale_fill_gradientn(colours = pal) +
  ggtheme_map()

ggsave("R2_100_25_Fine_plot.png",
       plot = Plot,
       width = 16,
       height = 8,
       units = "in",
       path = "/Volumes/DATA/JULIANO_NEYMAR/FishForVisa/Figures/"
)
